\LARGE \bf Artificial Cognition for Social Human-Robot Interaction:\\ An Implementation

### 2016-06-30 paper.tex
Update on Overleaf.

We also use shared plans to verbalise the sequence of actions and to explain
the human partner how a task may be shared~\cite{warnier2012when,fiore2016planning,milliez2016using}.

@@

\emph{Wasted time}: avoids plans where the human spends a lot
of its time being idle,

>>>>

The hierarchical structure of the shared plans obtained through the HTN refinement process provide a good basis for plan verbalization allowing the robot, when asked, to explain to its human partner how a task can be  shared~\cite{fiore2016planning,milliez2016using}.

@@

\emph{Wasted time}: avoids plans where the human spends a lot
of her/his time being idle,
